\chapter*{Joseph Warren Crandall}
\addcontentsline{toc}{chapter}{Vita}
\begin{singlespace}
\begin{center}
Email: jwcrandall@gwu.edu \\
GitHub ID: jwcrandall $\vert{}$ \href{http://www.josephcrandall.com}{josephcrandall.com}  \\
\href{http://www.linkedin.com/in/joseph-crandall-67003570}{LinkedIn} $\vert{}$ ORCid: 0000-0002-9684-9214 $\vert{}$ \href{https://scholar.google.com/citations?user=gUec2noAAAAJ\&hl=en}{Google Scholar}\\
\end{center}
\textbf{EDUCATION}\\
\textbf{The George Washington University}, Washington, DC\\
Master of Science, Electrical Engineering \hfill expected May 2019\\
Bachelor of Science, Computer Science and Physics \hfill May 2017\\
\textbf{Washington-Lee High School}, Arlington, Virginia\\
International Baccalaureate Full Diploma \hfill May 2012\\\\
\textbf{TECHNICAL SKILLS}\\
\textbf{Programming/Markup Languages \& Operating Systems}
\begin{itemize}
	\item Proficient with Arduino, C, C++, Java, Mathematica, MATLAB, Python, and LaTex
	\item Proficient with Linux, Mac OS, ROS
\end{itemize}
\textbf{Engineering Software}
\begin{itemize}
	\item Proficient with: Applied Flow Solutions (Fathom), AutoDesk (Revit), Cadence (Virtuoso), COMSOL (Multiphysics), Lumerical (Device, FDTD, Interconnect, Mode)
\end{itemize}
\textbf{Imaging/Clean Room}
\begin{itemize}
	\item Proficient with tools in \href{https://nic.gwu.edu/}{ GW NIC}
\begin{itemize}
	\item Contacts: Yigal Lilach – yigall@gwu.edu
\end{itemize}
\end{itemize}
\textbf{Robots Used}
\begin{itemize}
	\item Schunk LWA 4P
\begin{itemize}
	\item Contacts: Dr. Simha -- simha@gwu.edu
\end{itemize}
\end{itemize}

\textbf{PERSONAL PROJECTS}\\
\textbf{BRIEF}, Washington, DC \hfill  September 2016 -- 2017\\     
(Biological Robotics Imaging and Experimentation Framework)\\
\url{https://github.com/briefgw}\\
Contacts: Joseph Crandall - jwcrandall@gwu.edu
\begin{itemize}
	\item ROS based robot with a Gazebo simulation that is capable of imaging a sample via a point cloud from an Xbox Kinetic camera  and then transforming it into a mesh with the goal of perceiving a plant sample and then manipulating it with a Schuck Light Weight Arm over an extended period of time as the plant grows.
\end{itemize}
\textbf{Result:} \href{https://github.com/briefgw}{GitHub} \& \href{https://www.youtube.com/watch?v=my1lXeC_J6s&t=189s}{YouTube}
\\\\
\textbf{PROFESSIONAL WORK EXPERIENCES}\\
\textbf{GW OPEN Lab Research Assistant}, Washington DC \hfill  September 2017 - Current\\
\url{http://sorger.seas.gwu.edu/}\\
\url{https://github.com/openhpclgw}\\
Contact: Dr. Sorger - sorger@gwu.edu
\begin{itemize}
	\item Currently working on an optical array meant to improve upon a traditional all electric resistor array that is used to solve partial differential equations through analogue computation faster than with software by building fundamental physics equations into optical hardware. The initial problem we are trying to solve with ROC (Reconfigurable Optical Computer) is a Poisson heat transfer problem.
\end{itemize}
\textbf{Result:} \href{https://scholar.google.com/citations?user=gUec2noAAAAJ\&hl=en}{Google Scholar}\\
\textbf{ARUP Electrical Engineer Intern}, Washington DC \hfill June 2018 - August 2018\\
Contacts: Leyla Sadigh – leyla.sadigh@arup.com
\begin{itemize}
	\item Over the course of the summer I worked on 11 different projects as well as spent time doing training activities. I was able to see and work on a majority of the steps associated with a wework project from site visit to completion of sheets. Through that work I spent a great deal of time working on floor plans and reflected ceiling plans. I helped to build a load calculation excel sheet that can be used with exported Revit data to benchmark the accuracy of initial load approximations. 
\end{itemize}
\textbf{Result:} \href{https://www.youtube.com/watch?v=Q8VchT2CjtY&t=1s}{Final Presentation}\\
\textbf{ITER External Contractor}, Saint-Paul-les-Durance France \hfill June 2017-- July 2017\\
Nuclear fusion research and engineering summer internship\\
Contacts: Mr. Afzali – Lionel.Afzali@iter.org,\\
Dr. Moteleb – Moustafa.Moteleb@iter.org
\begin{itemize}
	\item Worked in the Tokamak Cooling Water System Division (TCWS) at ITER, utilizing AFT Fathom software to simulate fluid flow and heat exchange in the Primary Heat Transfer System (PHTS) prior to and after exiting the Vacuum Vessel (VV) with the goal of achieving desired temperatures and pressures at different points in the PHTS.  
\end{itemize}
\textbf{Result:} Submitted heat transfer report for TCWS. \href{https://www.youtube.com/watch?v=YTAHgalWx-k}{ITER Internship Video}\\
\textbf{Additive Manufacturing Research Assistant}, Knoxville TN \hfill	July 2016 – August 2016\\  
Higher Education Research Experience (HERE) at Oak Ridge National Laboratory\\
Contacts: Dr. List – listfaii@ornl.gov,\\ 
Dr. LeBlanc – sleblanc@gwu.edu
\begin{itemize}
	\item Milled stainless steel Bi2Te3 powder distribution system, accurate up to 100 micrometer powder layers, in order to validate the powder spreading component of an in development additive manufacturing selective laser melting system in order to manufacture more efficient Bi2Te3 based thermal electric converters.
\end{itemize}
\textbf{Result: }Developed powder bed distribution understanding for selective laser melting\\
\textbf{Nano-Technology Fellowship}, Washington DC \hfill May 2016 – July 2016\\
The George Washington University, funded through NSF\\
Contacts: Dr. LeBlanc – sleblanc@gwu.edu\\
Dr. Sorger – sorger@gwu.edu
\begin{itemize}
	\item Etched microfluidic channels through soft lithography process
	\item Manufactured nanoscale electronic lattice through electron beam lithography and liftoff process on silicon wafers.
	\item Imaged electronic lattice with SEM and AFM
\end{itemize}
\textbf{Result:} Acquired a proficiency in clean room and imaging machinery\\
\textbf{Robotics \& Computer Vision Researcher} \hfill September 2015 - May 2017\\
Washington DC\\
The George Washington University\\
Contacts: Dr. Simha – simha@gwu.edu\\
Dr. Choi - hchoi@gwu.edu
\begin{itemize}
	\item Developing robotic arm and hand system to pair with automated turn table to manipulate plant growth over time to better image plant development point cloud sensory data.
	\item Funded through NSF to attend Internet of Things (IOT) security conference in, Seoul, South Korea January 2016
\end{itemize}
\textbf{Result:} Added robotic biological manipulation capability through Robotic Operating System (ROS)
\\\\
\textbf{LEADERSHIP}\\
\textbf{Founder/Developer of Assistance.net} \hfill February 2013 - December 2014\\
Arlington, Virginia\\
18-month Start Up\\
\begin{itemize}
	\item Built a LAMP stack site using laravel framework.
	\item \url{https://github.com/jwcrandall/assistance.net}
	\item Developed business model for individual service provider market place website
	\item Organized team of developers; leased office space; incorporated in Delaware; negotiated contracts; set up physical server in Ashburn, Virginia; utilized AWS; produced promotional videos. 
\end{itemize}
\textbf{Result: } \href{https://www.youtube.com/watch?v=-9OBGa0BQKc&t=5s}{Website Demo} and \href{https://www.youtube.com/watch?v=kAH-ZZvkxP8&t=1s}{Website Promotion}
\\\\
\textbf{JOURNAL PUBLICATIONS}
\begin{itemize}
	\item Shuai Sun, Vikram K. Narayana, Ibrahim Sarpkaya, Joseph Crandall, Richard A. Soref, Tarek El-Ghazawi, Volker J. Sorger, "Hybrid Photonic-Plasmonic Non-blocking Broadband 5x5 Router for Optical Networks", IEEE Photonics Journal 2017.
\end{itemize}

\textbf{CONFERENCE TRANSACTIONS/PROCEEDINGS}
\begin{itemize}
	\item Tarek El-Ghazawi, Volker Sorger, Vikram K. Narayana, Jeff Anderson, Engin Kayraklioglu, Shuai Sun, Joseph Crandall, Yousra Alkabani, “Reconfigurable Optical Computer for Simulation of Physical Processes” April 6th 2018, 51st International Symposium on Microarchitecture 
	\item N. Batista, A. El Desouky, J. Crandall, S. Wang, J. Yang, S. LeBlanc, “Powder metallurgy characterization of thermoelectric materials for selective laser melting” March 2017 TechConnect World Innovation Conference
\end{itemize}

\textbf{CONFERENCES/PRESENTATION}\\
\textbf{2018 PIC International Conference} \hfill April 10 - 11th 2018\\
Brussels, Belgium
\begin{itemize}
	\item Creating and strengthening links between chipmakers and network builders for the photonic integrated circuit industry. 	
\end{itemize}
\textbf{2018 AIM Photonics Winter Academy} \hfill January 16 - 18th 2018\\
MIT Cambridge Massachusetts
\begin{itemize}
	\item A three day program with intensive short courses on integrated photonics: materials, devices, photonic integrated circuit layout, and chip fabrication. 
\end{itemize}
\textbf{2017 GW Research Days Showcase} \hfill April 4th 2017\\
Washington, DC
\begin{itemize}
	\item Presented poster titled “Particle Morphology Characterization of Bismuth Telluride (Bi2Te3) Powder for Additive Manufacturing”
\end{itemize}
\textbf{2017 GW SEAS R\&D Showcase} \hfill February 22nd 2017\\
Washington, DC
\begin{itemize}
	\item Presented poster titled “Particle Morphology Characterization of Bismuth Telluride (Bi2Te3) Powder for Additive Manufacturing”
\end{itemize}
\textbf{2016 Quadrennial Physics Congress} \hfill November 3rd - 5th  2016\\
San Francisco, California
\begin{itemize}
	\item Presented poster titled “Particle Morphology Characterization of Bismuth Telluride (Bi2Te3) Powder for Additive Manufacturing”
	\item Toured Stanford Linear Accelerator Center
\end{itemize}
\textbf{KISA-George Washington Univ. Joint Seminar on IoT Security} \hfill January 7th - 9th  2016\\
Seoul, Korea
\begin{itemize}
	\item Assisted in presentation on Authentication on Internet of Things (IoT) covering low complexity scalable authentication framework suitable for low power IoT environments and applications. 
	\item Toured Korean Internet \& Security Agency
\end{itemize}

\textbf{TEACHING}\\
\textbf{Teaching Assistant CSCI 3313 Foundations of Computing} \hfill Fall 2018 \& Fall 2017\\
The George Washington University\\
Professor: Hyeong-Ah Choi hchoi@gwu.edu\\
Students: 49(18), 45(17)\\
\url{https://github.com/jwcrandall/csci3313}
\begin{itemize}
	\item Theoretical: Automata Theory, Computability (solvable vs unsolvable problems), Complexity (computational easy vs. hard problems), Formal language theory, Chomsky Hierarchy (Regular languages, Context-free languages, Context-sensitive languages, Recursively enumerable languages)
	\item Laboratory: Write a mini-pascal compiler using Flex and Bison, and C
\end{itemize}
\textbf{Teaching Assistant CSCI 1121.10 Introduction to C Programming} \hfill Spring 2018\\
The George Washington University\\
Professor: Anrieta Draganova anri@gwmail.gwu.edu\\
Students: Total - 101 My Lab – 23\\
\url{https://github.com/jwcrandall/GA_CSCI_1121_Intro_C_Prog}
\begin{itemize}
	\item Theoretical: Structured programming with the C language. Control structures. Data types. Use of pointers. Matrix manipulation to solve simultaneous equations. External subroutines for mathematical and graphical applications. Introduction to C complex number representation.
\end{itemize}

\textbf{GRADUATE MERIT AWARDS}\\
\$6,000 GW ECE Graduate Research Assistantship      \hfill February 2019 - April 2019\\ 
\$11,520 GW GA Stipend Fellowship                   \hfill September 2018 - May 2019\\
\$2,400 GW GA Tuition Fellowship                    \hfill	September 2018 – December 2018\\
\$4,200 GW ECE Stipend Research Fellowship	        \hfill June 2018 - December 2018\\
\$4,200 GW ECE Stipend Research Fellowship	        \hfill November 2017-May 2018\\
\$12,000 GW CS Stipend Fellowship	                \hfill September 2017 – May 2018\\
\$4,000 GW CS Graduate Assistantship	            \hfill September 2017 – May 2018\\
\$1,500 GW ECE Stipend Fellowship                   \hfill June 2017 – August 2017\\
\$1,500 GW ECE Stipend Fellowship                   \hfill June 2017 – August 2017
\\\\
\textbf{LANGUAGE SKILLS}\\
English – native speaker\\	
Spanish – intermediate\\\\
\textbf{ACTIVITIES}\\
\begin{itemize}
	\item Rower and Member, Potomac Boat Club      \hfill July 2015 - Present  
\end{itemize}
\end{singlespace}
